Individual and Differential Harm in Redistricting

### 2022-08-27 paper/harm.Rmd
Update harm.Rmd

$$h_i(v,q,\tilde q) = \ind\{v(i) \neq \win_i(v, q)\} \ind\{v(i) = \win_i(v, \tilde q)\},$$

that is, a voter is harmed only if they are not represented by the candidate of their choice under $q$ but they would have been represented by their candidate of choice under the counterfactual plan $\tilde q$.
Notice the fundamental asymmetry in this definition: $h_i(v,q,\tilde q)\neq h_i(v,\tilde q,q)$.
Exchanging the role of the enacted plan and the counterfactual will not simply flip the direction of our conclusion.
In general, $q$ will harm some individuals while $\tilde q$, and $\tilde q$ will harm a different set of individuals.
A symmetric version of $h_i(v,q,\tilde q)$ would need to combine both of these groups: those harmed and those who gain by electing their chosen candidate under $q$ but not under the counterfactual $\tilde q$.
In practice, voters, courts, or politicians may find different balances in preventing harm and maximizing gains.

>>>>

$$h_i(v,q,\tilde q) = \ind\{v(i) \neq \win_i(v, q)\} \ind\{v(i) = \win_i(v, \tilde q)\}.$$

A voter is harmed only if they are not represented by the candidate of their choice under $q$ but they would have been represented by their candidate of choice under the counterfactual plan $\tilde q$.
Notice the fundamental asymmetry in this definition: $h_i(v,q,\tilde q)\neq h_i(v,\tilde q,q)$.
Exchanging the role of the enacted plan and the counterfactual will not simply flip the direction of our conclusion.
In general, $q$ will harm some individuals while $\tilde q$, and $\tilde q$ will harm a different set of individuals.
A symmetric version of $h_i(v,q,\tilde q)$ would need to combine both of these groups: those harmed and those who gain by electing their chosen candidate under $q$ but not under the counterfactual $\tilde q$.
In practice, voters, courts, or politicians may find different balances in preventing harm and maximizing gains.
